Resolvable Ambiguity

### 2019-07-10 paper/paper.tex
Small addition to Section 8.2

By using our implementation of the OCaml syntax to parse
real-world OCaml code, we can dynamically identify ambiguities in
the grammar presented in the reference manual.
%
For example, TODO: INSERT EXAMPLES.

@@

>>>>

By using our implementation of the OCaml syntax to parse
real-world OCaml code, we can dynamically identify ambiguities in
the grammar presented in the reference manual, instead of silently
resolving these in the implementation of an unambiguous parser.
%
For example, TODO: INSERT EXAMPLES.

@@

% TODO: State that we don't report exact numbers since we don't
% have the full language specified.
